---
title: "Code for the simulation D - random slopes, noncentered"
author: "benjamin simsa (benjamin.imsa@student.kuleuven.be)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import packages

```{r packages}
library(dplyr)
library(tidyr)
library(truncnorm)
library(nlme)
library(parameters)
library(lmerTest)
library(MASS)
library(here)
require(missMethods)
```

# Source the simulation functions

```{r }
source(here::here("code_custom_functions", "simulation_functions_missing_mcar.R"))
source(here::here("code_custom_functions", "simulation_functions_missing_block.R"))
source(here::here("code_custom_functions", "simulation_functions_missing_extreme_oneside.R"))
source(here::here("code_custom_functions", "simulation_functions_missing_extreme_twosided.R"))
```

# Variance of random slopes (autoregressive effects) = 0.05

## Data missing completely at random

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_04_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_04_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_04_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_04_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_03_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_06_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_06_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_06_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_06_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_08_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_08_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_08_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_08_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_10_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_10_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_03_10_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_03_10_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_04_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_04_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_04_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_04_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_05_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_06_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_06_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_06_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_06_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_05_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_08_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_08_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_08_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_08_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_05_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_10_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_10_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_05_07_10_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_05_07_10_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_05_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_05_07_10_100_100.rds"))
```

## Data missing in blocks

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_04_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_04_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_04_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_04_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_03_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_06_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_06_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_06_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_06_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_08_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_08_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_08_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_08_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_10_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_10_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_03_10_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_03_10_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_04_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_04_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_04_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_04_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_05_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_06_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_06_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_06_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_06_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_05_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_08_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_08_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_08_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_08_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_05_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_10_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_10_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_05_07_10_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_05_07_10_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_05_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_05_07_10_100_100.rds"))
```

## (1-compliance) lowest values set as missing (most extreme - one-sided)

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_04_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_04_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_04_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_04_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_03_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_06_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_06_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_06_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_06_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_08_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_08_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_08_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_08_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_10_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_10_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_10_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_03_10_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_04_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_04_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_04_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_04_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_05_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_06_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_06_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_06_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_06_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_05_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_08_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_08_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_08_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_08_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_05_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_10_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_10_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_10_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_05_07_10_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_05_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_05_07_10_100_100.rds"))
```

## (1-compliance)/2 lowest and highest values of each participant's process set as missing (most extreme -two-sided)

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_04_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_04_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_04_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_04_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_03_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_06_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_06_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_06_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_06_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_08_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_08_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_08_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_08_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_10_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_10_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_10_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_03_10_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_04_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_04_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_04_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_04_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_05_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_06_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_06_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_06_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_06_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_05_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_08_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_08_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_08_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_08_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_05_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_10_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_10_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_10_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_05_07_10_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.05), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_05_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_05_07_10_100_100.rds"))
```

# Variance of random slopes (autoregressive effects) = 0.1

## Data missing completely at random

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_04_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_04_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_04_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_04_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_03_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_06_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_06_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_06_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_06_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_06_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_08_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_08_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_08_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_08_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_10_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_10_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_03_10_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_03_10_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_04_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_04_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_04_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_04_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_mcar_10_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_06_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_06_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_06_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_06_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_mcar_10_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_08_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_08_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_08_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_08_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_mcar_10_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_10_20_50 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_10_20_100 = AR_simulate_missing_mcar(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_mcar_10_07_10_100_50 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_mcar_10_07_10_100_100 = AR_simulate_missing_mcar(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_mcar_10_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_mcar_10_07_10_100_100.rds"))
```

## Data missing in blocks

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_04_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_04_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_06_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_06_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_06_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_06_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_06_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_06_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_06_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_08_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_08_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_08_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_08_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_10_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_10_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_03_10_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_03_10_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_04_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_04_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_04_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_04_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_block_10_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_06_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_06_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_06_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_06_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_block_10_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_08_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_08_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_08_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_08_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_block_10_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_10_20_50 = AR_simulate_missing_block(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_10_20_100 = AR_simulate_missing_block(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_block_10_07_10_100_50 = AR_simulate_missing_block(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_block_10_07_10_100_100 = AR_simulate_missing_block(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_block_10_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_block_10_07_10_100_100.rds"))
```

## (1-compliance) lowest values set as missing (most extreme - one-sided)

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_04_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_04_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_04_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_06_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_06_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_06_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_06_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_06_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_06_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_08_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_08_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_08_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_08_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_10_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_10_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_10_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_03_10_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_04_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_04_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_04_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_04_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_oneside_10_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_06_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_06_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_06_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_06_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_oneside_10_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_08_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_08_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_08_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_08_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_oneside_10_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_10_20_50 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_10_20_100 = AR_simulate_missing_extreme_onesided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_10_100_50 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_oneside_10_07_10_100_100 = AR_simulate_missing_extreme_onesided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_oneside_10_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_oneside_10_07_10_100_100.rds"))
```

## (1-compliance)/2 lowest and highest values of each participant's process set as missing (most extreme -two-sided)

### AR = 0.3

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_04_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_03_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_04_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_03_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_04_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_03_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_04_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_03_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_06_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_03_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_06_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_03_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_06_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_03_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_06_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_03_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_08_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_03_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_08_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_03_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_08_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_03_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_08_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_03_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_10_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_03_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_10_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_03_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_10_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_03_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_03_10_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.3,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_03_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_03_10_100_100.rds"))
```

### AR = 0.7

#### Compliance = 0.4

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_04_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_07_04_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_04_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_04_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_07_04_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_04_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_04_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_07_04_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_04_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_04_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.4)


saveRDS(randslopes_extreme_twosided_10_07_04_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_04_100_100.rds"))
```

#### Compliance = 0.6

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_06_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_07_06_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_06_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_06_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_07_06_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_06_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_06_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_07_06_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_06_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_06_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.6)


saveRDS(randslopes_extreme_twosided_10_07_06_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_06_100_100.rds"))
```

#### Compliance = 0.8

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_08_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_07_08_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_08_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_08_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_07_08_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_08_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_08_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_07_08_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_08_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_08_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 0.8)


saveRDS(randslopes_extreme_twosided_10_07_08_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_08_100_100.rds"))
```

#### Compliance = 1

##### N = 20, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_10_20_50 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_07_10_20_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_10_20_50.rds"))
```

##### N = 20, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_10_20_100 = AR_simulate_missing_extreme_twosided(N = 20,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_07_10_20_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_10_20_100.rds"))
```

##### N = 100, T = 50

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_10_100_50 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 50,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_07_10_100_50, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_10_100_50.rds"))
```

##### N = 100, T = 100

```{r}
set.seed(4)

randslopes_extreme_twosided_10_07_10_100_100 = AR_simulate_missing_extreme_twosided(N = 100,
                    T.obs = 100,
                    Ylag.center = FALSE,
                    b00 = 0, estimate_randomslopes = TRUE,
                    b10 = 0.7,
                    sigma = sqrt(3), 
                    rho = 0, 
                    sigma.v0 = sqrt(3), 
                    sigma.v1 = sqrt(0.1), 
                    rho.v = 0, 
                    alpha = 0.05, 
                    R = 1000, 
                    compliance_mean = 1)


saveRDS(randslopes_extreme_twosided_10_07_10_100_100, file = here::here("results", "sim_d_randomslopes_noncentered", "randslopes_extreme_twosided_10_07_10_100_100.rds"))
```
